---
title: "Capstone Project Proposal:Bitcoin"
output: html_document
---
```{r, echo=FALSE}
load(file="Bitcoin.RData")

```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### What is the problem you want to solve?

Some have speculated that **bitcoin** or other crypto currencies are gaining popularity and may one day take over or somehow integrate into our current financial system. Bitcoin appreciation or strength could indicate a growing popularity and thus more *interference* with our current currency markets. I want to forecast the future price of bitcoin to see if it will gain enough demand to take market share away from traditional financial institutions (FI's) or possibly become a primary currency for some.

### Who is your client and why do they care about this problem? 

FI's will be interested in this information because it could *transform* the banking industry. Currently within the US, the financial services industry is centralized and regulated by the Federal Reserve. Since bitcoin is a decentralized form of digital currency, it's use within the US could cause changes in regulation relating to all FI's. On top of that, it could steer consumers away from using traditional FI's making this forecast very valuable for future business strategies in the financial services industry.

### What data are you going to use for this? How will you acquire this data?

The data I am going to use is historical pricing of Bitcoin which I obtained from [Kaggle.com]( 
https://www.kaggle.com/sudalairajkumar/cryptocurrencypricehistory)

```{r bitcoin_price, echo=FALSE}
summary(bitcoin_price)
```

### Outline your approach to solving this problem (knowing that this might change later).

My approach will be to use linear regression to forecast future pricing and determine if the price will appreciation enough to affect major FI's. 